Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-24 Paper/gammaRays.tex
Drafted Model Description section

The main idea behind our model is to assume that the burst opening angle depends on energy of emitted photons, or, equivalently, that the most energetic plasma particles are concentrated near the axis of the jet, while low energy particle are on the periphery.
As you can see on figure \ref{fig:modelOverview} this leads to a time stretching effect in some cases due to relativistic beaming.

@@

First of all, the number of observed GRBs rapidly decreases with energy.
There are around 750 bursts detected by GBM in hard X-rays and low energy gamma rays, and only 4

>>>>

The main idea behind our model is to assume that the burst opening angle depends on energy of emitted photons, or, equivalently, that the most energetic plasma particles are concentrated near the axis of the jet, while low energy particles are on the periphery.
As you can see on figure \ref{fig:modelOverview} this leads to a time stretching effect in some cases due to relativistic beaming.

@@

First of all, the number of observed GRBs rapidly decreases with energy.
There are around 750 bursts detected by GBM in hard X-rays and low energy gamma rays \cite{Vianello:2013ela} (half of them were in a LAT field of view), only 30 or so were detected by LAT above \unit[100]{MeV}, and only about 4 of them were detected above GeV.
This observation is hard to explain in a framework of uniform jet model given that burst energetics are similar \cite{Bloom:2003wy}.
It is, however, easy to explain in our model, given that small observation angles are rare, and the only way to produce high energy radiation is to have the observation angle small enough.

Another argument comes from consideration of processes happening in jets, specifically the scattering of particles near the jet boundary.
While plasma particles scatter, they simultaneously lose energy, and change directions, sometimes propagating beyond the jet boundary, and therefore increasing the jet opening angle.
So, the processes of energy loss and increase of jet size are correlated, therefore the low energy particles should be closer to the jet boundary.

In the following sections we will rigorously derive the procedure for computing time stretching factors from our model, and compare them to observations obtained in the previous section.
